Evaluating Covid-19 Short-Term Forecasts using \pkg{scoringutils} in \proglang{R}

### 2021-03-06 article.Rnw
shorten section about forecast types and add figure

\subsection{Forecast types}

In its most general sense, a forecast is the forecaster’s stated belief about the future \citep{gneitingStrictlyProperScoring2007}. For conceptual clarity, it is however useful to distinguish between different types of forecasts. In terms of the quantitative forecasts that can be evaluated with \pkg{soringutils}, we can distinguish point forecasts from probabilistic forecasts. A point forecast states a single number and is the simplest form of a forecast. It is limited in its usefulness, as it does not give information about the uncertainty of the forecast. A very certain forecast may, for example, warrant a very different course of actions than does a very uncertain one. A probabilistic forecast, in contrast, is a forecast made in terms of the entire predictive distribution. Providing the entire predictive distribution allows the forecaster to express their belief about all aspects of the underlying data-generating distribution (including e.g. skewness or the width of its tails). Probabilistic forecasts are therefore the focus of this paper as well as the \pkg{scoringutils} package.

\subsection{Forecast formats}

Not only can we distinguish different forecast types, but also different formats in which predictions may be reported. This distinction is important, as different formats and prediction types require slightly different evaluation approaches. Forecasts can be expressed analytically in a closed form, or more commonly through either predictive samples or quantiles. Predictive samples are useful if no closed-form predictive distribution is available, but require a lot of storage space. They may also come with a loss of precision that is especially pronounced in the tails of the predictive distribution, where quite a lot of samples are needed to accurately characterise the distribution. For that reason, often quantiles are reported instead [citation FORECAST HUBS]. As an alternative representation of a quantile forecast, one can also express predictions using central prediction intervals. In this case, the forecaster reports a range to denote the interval as well as a value for the lower and upper bound. A forecaster could also in principle state their forecasts in a binary way by defining an outcome and assigning a probability that the outcome will come true. This type of forecasting is common in many classification problems. If we think of the outcome of some number being larger or smaller than a certain value, we can immediately see the connection between binary predictions and the concept of a cumulative distribution functions (CDF). All of these forecast types can be evaluated using \pkg{scoringutils}. The general forecasting paradigm [GNEITING] that guides the evaluation process is the same irrespective of the reporting format, even though specific scoring metrics differ.

@@

\input{tables/scores-table.tex}

>>>>

\subsection{Forecast types and forecast formats}

In its most general sense, a forecast is the forecaster’s stated belief about the future \citep{gneitingStrictlyProperScoring2007} that can come in many different forms. Quantitative forecasts are either point forecasts or probabilistic in nature and can make statements about continuous, discrete or binary outcome variables. Point forecasts only give one single number for the most likely outcome, but do not quantify the forecaster's uncertainty. This limits their usefulness, as a very certain forecast may, for example, warrant a very different course of actions than does a very uncertain one. Probabilistic forecasts, in contrast, by definition provide a full predictive distribution. This makes them much more useful in any applied setting, as we learn about the forecaster's uncertainty and their belief about all aspects of the underlying data-generating distribution (including e.g. skewness or the width of its tails). Probabilistic forecasts are therefore the focus of this paper as well as the \pkg{scoringutils} package.

The predictive distribution of a probabilistic forecast can be represented in different ways with implications for the appropriate evaluation approach. Forecasts can wither be expressed analytically in a closed form, or more commonly through either predictive samples or quantiles. Predictive samples are useful if no closed-form predictive distribution is available, but require a lot of storage space. They may also come with a loss of precision that is especially pronounced in the tails of the predictive distribution, where quite a lot of samples are needed to accurately characterise the distribution. For that reason, often quantiles or central prediction intervals are reported instead [citation FORECAST HUBS]. For binary prediction targets, common in many classification problems, a probabilistic forecasts is represented by the probability that an outcome will come true. DO I NEED TO TALK ABOUT MULTINOMIAL CLASSIFICATION PROBLEMS? Figure \ref{fig:overview-forecast-types} summarises the different forecast types and formats. The general forecasting paradigm [GNEITING], however, that guides the evaluation process is the same irrespective of the reporting format, even though specific scoring metrics differ.

\begin{figure}[h]
\centering
\includegraphics{plots/overview-forecast-types.png}
\caption{\label{fig:overview-forecast-types} Overview of forecast types}
\end{figure}

@@

% \input{tables/scores-table.tex}
